Home

### 2017-02-01 analysis/index.Rmd
Files commited by wflow_commit.

Click on this [link](first-analysis.html) to see my results.

The goal of this new template is to simplify the setup and maintenance of a research website.
Specifically,

*  Easier to build and extend the website using the new tools in the [rmarkdown][] package and [latest RStudio release][rstudio]
*  Easier to deploy the website with Git and GitHub by only using one branch

[rmarkdown]: http://rmarkdown.rstudio.com/rmarkdown_websites.htm
[rstudio]: https://www.rstudio.com/products/rstudio/download/preview/

>>>>

Click on this [orthogonal CV](miss_position.html) to see my example.
